\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{lmodern}

% Color definitions
\definecolor{headercolor}{RGB}{0,0,0}
\definecolor{sectioncolor}{RGB}{0,102,204}

% Formatting
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Section formatting
\titleformat{\section}{\Large\bfseries\color{sectioncolor}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{6pt}

\titleformat{\subsection}{\bfseries}{}{0em}{}
\titlespacing*{\subsection}{0pt}{6pt}{2pt}

% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \textit{#2} \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}
  \vspace{-4pt}
}

\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\begin{document}

% Header
\begin{center}
    {\Huge\bfseries Juan Huaco} \\[4pt]
    {\large AI Developer | Full Stack Developer } \\[6pt]
    \small
    \faEnvelope\ \href{mailto:jphuaco@gmail.com}{jphuaco@gmail.com} \quad
    \faLinkedin\ \href{https://linkedin.com/in/juanhuaco}{linkedin.com/in/juanhuaco} \quad
    \faGithub\ \href{https://github.com/juanhuaco}{github.com/juanhuaco} \quad
    \faGlobe\ \href{https://juanhuaco.com}{juanhuaco.com}
\end{center}

\vspace{-8pt}

% Profile
\section{Professional Summary}
\small
Full Stack Developer with 2+ years of experience specializing in AI solutions, MCP development, RAG systems, and scalable application architecture. Proven expertise in extending LLM capabilities using FastMCP and Python, developing intelligent systems with LangChain, and building robust backend solutions. Strong background in API integrations, OAuth implementations, and workflow orchestration. Passionate about leveraging AI technologies to solve complex business problems and deliver innovative software products.

% Skills
\section{Technical Skills}
\small
\begin{itemize}[leftmargin=0.15in, itemsep=1pt, parsep=0pt]
    \item \textbf{AI Development:} Python, FastMCP, LangChain, RAG Systems, Vector Databases, MCP Servers, LLM Integration, Prompt Engineering
    \item \textbf{Backend Development:} FastAPI, Laravel, RESTful APIs, PostgreSQL, SQL Server, MongoDB, Elasticsearch, Eloquent ORM, OAuth
    \item \textbf{Frontend Development:} Svelte, TypeScript, JavaScript, Tailwind CSS, WordPress, Elementor
    \item \textbf{Tools \& Workflows:} Apache Airflow, Docker, Git, Redmine, Postman, Cursor, VS Code, CI/CD, AS2 Protocol
\end{itemize}

% Experience
\section{Professional Experience}

\resumeSubheading
{AI Developer}{Present}
{Intelligence Company (U.S.)}{Remote}
\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt, parsep=0pt]
    \resumeItem{Developing Model Context Protocol (MCP) solutions using FastMCP and Python to extend LLM capabilities and enable seamless integration between AI models and external systems.}
    \resumeItem{Building custom MCP servers and tools that connect large language models to databases, APIs, and enterprise data sources, enabling context-aware AI applications.}
    \resumeItem{Implementing scalable Python-based backends integrating Elasticsearch and MongoDB for efficient data storage and retrieval operations.}
    \resumeItem{Designing RESTful APIs and backend services to support real-time querying and intelligence reporting systems.}
\end{itemize}

\resumeSubheading
{Full Stack Developer}{6 months}
{Logistics Technology Company}{Argentina \& Chile}
\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt, parsep=0pt]
    \resumeItem{\textbf{Mercado Libre API Integration:} Architected and developed a complete OAuth-based integration system using Laravel and Svelte, implementing secure authentication flows, automated token refresh mechanisms, and bidirectional data synchronization with Mercado Libre's order and shipment APIs. Deployed containerized application using Docker and PostgreSQL.}
    \resumeItem{\textbf{Supply Chain Integration:} Developed critical API endpoints for supply chain integration between international clients and logistics providers. Built custom Svelte toolkit for API testing and validation. Optimized SQL queries and stored procedures, achieving 3x improvement in execution speed.}
    \resumeItem{Technologies: Laravel 12, Svelte 5, Docker, PostgreSQL, SQL Server, RESTful APIs, AS2 Protocol, Eloquent ORM}
\end{itemize}

\resumeSubheading
{AI Developer - RAG Systems}{3 months}
{Technology Company}{Argentina}
\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt, parsep=0pt]
    \resumeItem{Designed and implemented Retrieval-Augmented Generation (RAG) systems using LangChain, enabling intelligent document retrieval and context-aware AI responses for enterprise applications.}
    \resumeItem{Architected Apache Airflow workflows for automated data processing pipelines, orchestrating ETL operations and ensuring reliable data flow for AI model training and inference.}
    \resumeItem{Developed vector database integrations and embedding strategies to optimize semantic search capabilities and improve retrieval accuracy for RAG applications.}
    \resumeItem{Technologies: Python, LangChain, Apache Airflow, Vector Databases, NLP, FastAPI, PostgreSQL}
\end{itemize}

\resumeSubheading
{Laboratory Management Assistant}{1 year 8 months}
{Universidad Tecnológica Nacional - FRSF}{Argentina}
\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt, parsep=0pt]
    \resumeItem{Managed technical support operations for over 10 support assistants using Redmine for ticket prioritization and task management.}
    \resumeItem{Maintained and optimized performance of 60+ computers across multiple laboratories, ensuring minimal downtime and supporting 20+ university courses with software installation and updates.}
    \resumeItem{Technologies: Redmine, Remote Desktop, Windows, Linux}
\end{itemize}

\resumeSubheading
{Web Developer}{9 months}
{Niloft}{Argentina}
\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt, parsep=0pt]
    \resumeItem{Designed and developed responsive, user-friendly websites using WordPress and Elementor, focusing on visual appeal and optimal user experience.}
    \resumeItem{Customized themes and optimized website performance for improved user engagement and functionality.}
    \resumeItem{Technologies: WordPress, Elementor, Web Design, UI/UX}
\end{itemize}

% Education
\section{Education}
\resumeSubheading
{Systems Engineering (Final Project in Progress)}{Expected 2026}
{Universidad Tecnológica Nacional - Facultad Regional Santa Fe}{Santa Fe, Argentina}

\vspace{4pt}

\textbf{Relevant Coursework:} Innovation in NLP, Generative AI, and Knowledge Graphs (2024) | Numerical Methods \& Optimization | Signal Processing \& Analysis | Data Structures \& Algorithms

% Languages
\section{Languages}
\small
\textbf{Spanish:} Native \quad | \quad \textbf{English:} Upper-Intermediate (B2) \quad | \quad \textbf{Portuguese:} Upper-Intermediate (B2) \quad | \quad \textbf{German:} Elementary (A1)

\end{document}

